Alex's Notes and Text Fragments for the JOSS Manuscript

### 2021-05-02 paper/paper.Rmd
add spatial disc description

>>>>

Another buffering oriented resampling method is "Spatial Disc" from package \pkg{sperrorest}.
The name spins from "Leave-one-disc-out" which again originates from the generic "Leave-one-out" method.
More specifically, the 'disc' which is being left our here refers to the radial area of test sets created from this method.

Around the radial test set a buffer zone / neutral area can be defined in which observations are excluded from the training set, increasing the spatial distance between train and test sets.

```{r disc, fig.cap="Visualization of 'Spatial Disc' method.", out.width="50%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 200L, buffer = 300L)
resampling_disc$instantiate(task)

autoplot(resampling_disc,
  size = 0.8, task = task, fold_id = 1, crs = 32717) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
